---
title: "Annex Chapter 4"
author: "Juan Pablo Bertucci"
date: "28 November 2019"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("readr")
library("purrr")
library("caret")
library("tibble")
library("tidyverse")
```

## Input data

The data collected for the section defined is imported below

```{r message=FALSE, warning=FALSE}
data=read_csv(file = "C:/Users/Juan Pablo/OneDrive - University of Illinois - Urbana/Fall 2019/CEE 508 - Pavement Evaluation and Rehabilitation/Term Project/DATA/irivspci2.csv",col_names = T)
data=as_tibble(data)
```

## Models
We try first a linear model, then a nearest neighbour model, and then a random forest model to analyse possible machine learning approaches.

### Linear Model

```{r}
fit_lm=lm(pci~iri, data = data)

summary(fit_lm)

plot(fit_lm)
grid()
```

### Nearest Neighbors

```{r }
fit_knn = train(
  pci ~ iri,
  data = data,
  method = "knn",
  trControl = trainControl(method='cv',number = 5)
  )

fit_knn

fit_knn$results

plot(fit_knn)

```

### Random Forest

```{r  message=FALSE, warning=FALSE}
fit_rf = train(
  pci ~ iri+st,
  data = data,
  method = "rf",
  trControl = trainControl(method='cv',number = 5)
  )

fit_rf

fit_rf$results

fit_rf$finalModel

plot(fit_rf)
```

## Predicted vs. Observed Values

The predicting quality of each model is shown below contrasting the observed and predicted values.

```{r echo = FALSE}
plot(predict(fit_lm, data), data$pci,
     xlim = c(0, 100), ylim = c(0, 100), pch = 20, col = "darkgrey",
     xlab = "Predicted", ylab = "Actual",
     main = "Linear Model")
abline(a = 0, b = 1, col = "green")
grid()
```

```{r echo = FALSE}
plot(predict(fit_knn, data), data$pci,
     xlim = c(0, 100), ylim = c(0, 100), pch = 20, col = "darkgrey",
     xlab = "Predicted", ylab = "Actual",
     main = "KNN Model")
abline(a = 0, b = 1, col = "red")
grid()
```

```{r echo = FALSE}
plot(predict(fit_rf, data), data$pci,
     xlim = c(0, 100), ylim = c(0, 100), pch = 20, col = "darkgrey",
     xlab = "Predicted", ylab = "Actual",
     main = "Forest Model")
abline(a = 0, b = 1, col = "blue")
grid()
```
